Template \aastex Article with Examples: v6.3\footnote{Released on June, 10th, 2019}

### 2020-04-28 writeups/Su_disk_disp.tex
redo even more plots

When $\theta_{\rm sd, i}\neq 0$, \textcolor{Corr}{we find that the final
obliquity $\theta_{\rm f}$ varies over a range of values for a given
$\theta_{\rm sd, i}$, as can be seen in Fig.~\ref{fig:nonad_3_ensemble}. The
range can be described by}
\begin{equation}
    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
        \lesssim \theta_{\rm f}
        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
    .\label{eq:nonad_q_f_dist}
\end{equation}
\textcolor{Corr}{
This can be understood as follows (see Fig.~\ref{fig:2nonadrot}). In the
beginning ($\eta = \eta_{\rm i} \gg 1$), the initial spin vector precesses
around $\uv{l}_{\rm d}$ on a cone with opening half-angle $\theta_{\rm sd, i}$
(more precisely, the cone is centered on CS2, which coincides with $\uv{l}_{\rm
d}$ as $\eta_{\rm i} \to \infty$). Note that for $\eta \gg 1$, the adiabaticity
condition is easily satisfied: Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}} \sim
\epsilon \tan\p{\theta_2 - I} \ll \eta$. As $\eta$ decreases, the system will
transition from being adiabatic to being nonadiabatic, since $\epsilon \gtrsim
\epsilon_{\rm c}$. The evolution of the system can thus be decomposed into
two phases: (i) when the evolution is adiabatic, the spin vector will precess
around the slowly-moving CS2, then (ii) when the evolution becomes nonadiabatic,
the spin vector stops tracking the quickly-evolving CS2. During the adiabatic
evolution of phase (i), the angle between CS2 and the spin vector is
approximately unchanged due to conservation of phase space area}\footnote{
\textcolor{Corr}{This approximation assumes sufficiently small $\theta_{\rm sd,
i}$ such that libration about CS2 remains approximately circular throughout
phase (i). Deviations from this approximation occur when $\theta_{\rm sd, i}$ is
sufficiently large that libration cycles become non-circular as $\eta$ decreases
(Fig.~\ref{fig:eq_1contours} illustrates that libration cycles farther from CS2
are less circular).
% Such deformations decrease the obliquity spanned by the cone (see
% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
% correspond to bases of cones), which causes the observed range of final
% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
This causes the deviation of the data in Fig.~\ref{fig:nonad_3_ensemble} from
Eq.~\eqref{eq:nonad_q_f_dist} for $\theta_{\rm sd, i} \gtrsim 45^\circ$.
}}.
\textcolor{Corr}{Once the evolution enters phase (ii), the precession axis
quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta
\to \eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
obliquity, so the range of obliquities when the spin vector stops tracking CS2
is frozen in as the range of final obliquities.}

>>>>

When $\theta_{\rm sd, i}\neq 0$, \textcolor{Corr}{we find that the final
obliquity $\theta_{\rm f}$ varies over a range of values for a given
$\theta_{\rm sd, i}$, as can be seen in Fig.~\ref{fig:nonad_3_ensemble}. The
range can be described by}
\begin{equation}
    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
        \lesssim \theta_{\rm f}
        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
    .\label{eq:nonad_q_f_dist}
\end{equation}
\textcolor{Corr}{
This can be understood as follows (see Fig.~\ref{fig:2nonadrot}). In the
beginning ($\eta = \eta_{\rm i} \gg 1$), the initial spin vector precesses
around $\uv{l}_{\rm d}$ on a cone with opening half-angle $\theta_{\rm sd, i}$
(more precisely, the cone is centered on CS2, which coincides with $\uv{l}_{\rm
d}$ as $\eta_{\rm i} \to \infty$). Note that for $\eta \gg 1$, the adiabaticity
condition is easily satisfied: Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}} \sim
\epsilon \tan\p{\theta_2 - I} \ll \eta$. As $\eta$ decreases, the system will
transition from being adiabatic to being nonadiabatic, since $\epsilon \gtrsim
\epsilon_{\rm c}$. The evolution of the system can thus be decomposed into
two phases: (i) when the evolution is adiabatic, the spin vector will precess
around the slowly-moving CS2, then (ii) when the evolution becomes nonadiabatic,
the spin vector stops tracking the quickly-evolving CS2. During the adiabatic
evolution of phase (i), the angle between CS2 and the spin vector is
approximately unchanged due to conservation of phase space area}\footnote{
\textcolor{Corr}{This approximation assumes sufficiently small $\theta_{\rm sd,
i}$ such that libration about CS2 remains approximately circular throughout
phase (i) (initially, when $\eta \to \infty$, all librations are circular about
$\uv{l}_{\rm d}$). This assumption breaks down when $\theta_{\rm sd, i}$ is
sufficiently large that librating orbits become non-circular as $\eta$ decreases
before the end of phase (i) (Fig.~\ref{fig:eq_1contours} illustrates that
libration cycles farther from CS2, corresponding to a larger $\theta_{\rm sd,
i}$, are less circular for a given $\eta$).
% Such deformations decrease the obliquity spanned by the cone (see
% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
% correspond to bases of cones), which causes the observed range of final
% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
This causes the deviation of the data in Fig.~\ref{fig:nonad_3_ensemble} from
Eq.~\eqref{eq:nonad_q_f_dist} for $\theta_{\rm sd, i} \gtrsim 45^\circ$.
}}.
\textcolor{Corr}{Once the evolution enters phase (ii), the precession axis
quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta
\to \eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
obliquity, so the range of obliquities at the end of phase (i) is frozen in as
the range of final obliquities.}
